REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-12-21 main.tex
scribbled some notes for binary section

>>>>

Most (word) models, including this work, of feedback and chemical evolution in galaxies ignore the effects of binary star evolution, generating feedback and yields from stellar populations that are comprised of many single stars. There are two effects that could significantly influence galaxy evolution: 1) radiation, and 2) runaway stars. The former could greatly increase the impact radiation feedback has on the galaxy, but its exact role is unclear since the photons emitted durign the extended lifetime are more likely to escape the galaxy (check this). The latter, however, could influence the typical regions where supernovae occur, as stars can travel appreciably far from their birth cloud (distance) before exploding, changing the effect of feedback and (yields). Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochasitcally assigning binary star properties to some subset of our individual stars. This is beyond the scope of this project, but will be investigated in future works.
